---
title: "p8105_hw2_xz3078"
author: Xinyi Zhou
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
```
# Problem 1

```{r}
Trashwheel = 
  read_excel("./data/Trashwheel.xlsx", sheet = 1, range = "A2:N535") %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(sports_balls = round(sports_balls, 0))
Trashwheel
```

```{r}
Precipitation_2018 = 
  read_excel("./data/Trashwheel.xlsx", sheet = 7, range = "A2:B14") %>%
  janitor::clean_names() %>%
  mutate(year = 2018)

Precipitation_2019 = 
  read_excel("./data/Trashwheel.xlsx", sheet = 6, range = "A2:B14") %>%
  janitor::clean_names() %>%
  mutate(year = 2019)

Precipitation_tidy = 
  bind_rows(Precipitation_2018, Precipitation_2019) %>%
  mutate(month = month.name[as.numeric(month)]) %>%
  select(year, everything())
Precipitation_tidy
```

The total number of observations in "Trashwheel" dataset is `r nrow(Trashwheel)`, with variables `r colnames(Trashwheel)`. The total number of observation in "Precipitation_tidy" dataset is `r nrow(Precipitation_tidy)`, with variables `r colnames(Precipitation_tidy)` precipition.

For available data, the total precipitation in 2018 is `r sum(pull(Precipitation_2018, total))`. The median number of sports balls in a dumpster in 2019 is `r median(pull(filter(Trashwheel, year == 2019), sports_balls))`. 

# Problem 2
```{r message = FALSE}
pols_month = 
  read_csv("./data/fivethirtyeight_datasets/pols-month.csv") %>%
  separate(mon, into = c("year", "month", "day")) %>%
  mutate(month = month.name[as.numeric(month)], 
         year = as.numeric(year),
         president = recode(prez_dem, `0` = "gop", `1` = "dem")) %>%
  select(-day, -prez_dem, -prez_gop) %>%
  arrange(year, month) 
pols_month
```

```{r message = FALSE}
snp=
  read_csv("./data/fivethirtyeight_datasets/snp.csv") %>%
  mutate(date = mdy(date)) %>%
  separate(date, into = c("year", "month", "day")) %>%
  mutate(month = month.name[as.numeric(month)]) %>%
  mutate(year = as.numeric(year),
    year = ifelse(year > 2021, year - 100, year)) %>%
  select(-day) %>%
  arrange(year, month)
snp
```

```{r message = FALSE}
unemployment=
  read_csv("./data/fivethirtyeight_datasets/unemployment.csv") %>%
  pivot_longer(
    Jan:Dec,
    names_to = "month", 
    values_to = "percentage") %>%
  mutate(month = match(month,month.abb),
         month = month.name[as.numeric(month)]) %>%
  janitor::clean_names()
unemployment
```

```{r}
join_pols_snp = 
  left_join(pols_month, snp, by = c("year", "month"))
join_pols_snp
```

```{r}
join_all = 
  left_join(join_pols_snp, unemployment, by = c("year", "month"))
join_all
```

In dataset "pols_month", there are `r nrow(pols_month)` observations, the range of year is from `r min(pull(pols_month,year))` to `r max(pull(pols_month,year))` with variables `r colnames(pols_month)`. In dataset "snp", there are `r nrow(snp)` observations, the range of year is from `r min(pull(snp,year))` to `r max(pull(snp,year))` with variable `r colnames(snp[3])` which means the closing values of the S&P stock index on the associated date. In dataset "unemployment", there are `r nrow(unemployment)` observations, the range of year is from `r min(pull(unemployment,year))` to `r max(pull(unemployment,year))` with variables `r colnames(unemployment[3])` which means the percentage of unemployment in the associated month of the associated year. 

In the merged dataset "join_all", there are `r nrow(join_all)` observations and `r ncol(join_all)` columns, the range of year is from `r min(pull(join_all,year))` to `r max(pull(join_all,year))`. 

# Problem 3


