---
title: "p8105_hw2_xz3078"
author: Xinyi Zhou
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
```
# Problem 1

```{r}
Trashwheel = 
  read_excel("./data/Trashwheel.xlsx", sheet = 1, range = "A2:N535") %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(sports_balls = round(sports_balls, 0))
Trashwheel
```

```{r}
Precipitation_2018 = 
  read_excel("./data/Trashwheel.xlsx", sheet = 7, range = "A2:B14") %>%
  janitor::clean_names() %>%
  mutate(year = 2018)

Precipitation_2019 = 
  read_excel("./data/Trashwheel.xlsx", sheet = 6, range = "A2:B14") %>%
  janitor::clean_names() %>%
  mutate(year = 2019)

Precipitation_tidy = 
  bind_rows(Precipitation_2018, Precipitation_2019) %>%
  mutate(month = month.name[as.numeric(month)]) %>%
  select(year, everything())
Precipitation_tidy
```

The total number of observations in "Trashwheel" dataset is `r nrow(Trashwheel)`, with variable `r colnames(Trashwheel)`. The total number of observation in "Precipitation_tidy" dataset is `r nrow(Precipitation_tidy)`, with variable `r colnames(Precipitation_tidy)`.

For available data, the total precipitation in 2018 is `r sum(pull(Precipitation_2018, total))`. The median number of sports balls in a dumpster in 2019 is `r median(pull(filter(Trashwheel, year == 2019), sports_balls))`. 


